---
title: "Paper 2 Measures and Analysis"
output: html_notebook
---

There are **6 independent variables and 2 dependent variables** specified by the conceptual framework:   

* Business model level:  
    + Value proposition differentiation  
    + Client segmentation  
    + Network differentiation  
    + Revenue model differentiation  
* Contextual level:   
    + Venture separation  
    + Integrated organizational culture  
* Performance:   
    + Creative performance  
    + Business performance  

These are **the items used** in order to measure them:   

| Variable | Survey items used | 
|----------------------------------------------------------------------------------------------------------------------------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------|
| **Value proposition differentiation** (VPDIF) | Some types of our services and products help reaching our financial and business goals, while others contribute to our creative goals.  |
| **Client segmentation** (SEGM) | Some client segments are commercial and bring in money, while others secure creative work, reputation and exposure. |
| **Network differentiation** (NETWDIF) | We make a clear distinction between creative and business partners. |
|**Diversification of revenue models** (REVDIF) | Different revenue models and conditions are used for commercial projects and the projects we perceive as creative and/or challenging. | 
| **Venture separation** (SPINDIF) |           |
|  *Composite measure (creative OR commercial affiliate venture Y/N, minimum of the following items).* | The other venture(s) connected to our firm focus(es) on the more commercial and/or entrepreneurial work. |
|     | The other venture(s) connected to our firm focus(es) on the more creative projects, as opposed to the commercial and entrepreneurial work. |  
| **Integrated culture** (INTCULT)|     |
| *Composite measure (the mean of the following items).* | When it comes to our activities and processes, we always try to develop synergies and interactions between the creative and business-related aspects.  | 
|     | When making decisions within our company, we seek synergies, integration, and compromises between our creative and commercial ambitions.  |  
| **Business performance** (BP)|       |
| *Composite measure (the mean of the following items, compared to main competotors).*   | Gross profits per partner | 
|     | Gross margin on provided services |  
|     | Growth in profits | 
| **Creative performance** (CP)|          |
| *Composite measure (the mean of the following items, compared to main competotors).*   | Producing highly innovative work | 
|     | Working on projects that challenge the boundaries of the field |  
|     | Working on projects that match the firm's creative and professional aspirations |   
|     | Creating the desired impact with its work |  

These are **the descriptive statistics** for each variable: 
```{r setup data, echo=FALSE, warning=FALSE}
bots<- read.csv("~/Dropbox/1PhD/Articles/Survey Data/bots_renamed.csv") 
myraw <- bots[,c("X1", "paradox_DIF1", "paradox_DIF3", "paradox_DIF4", 
               "paradox_DIF5", "spin_Commercial", "spin_Creative", "paradox_INT6", "paradox_INT2","CP", "BP")]
myraw$INTCULT <- rowMeans(myraw[,c("paradox_INT6", "paradox_INT2")])
myraw$SPINDIF <- pmax(myraw$spin_Commercial, myraw$spin_Creative)
newnames <- c("ID", "VPDIF", "SEGM", "NETWDIF", "REVDIF") 
colnames(myraw)[1:5] <- newnames
psych::describe(myraw[,c("VPDIF", "SEGM", "NETWDIF", "REVDIF", "SPINDIF", "INTCULT", "CP", "BP")])
```

This is **the correlation matrix** for all variables used: 

```{r correlation matrix, echo=FALSE, warning=FALSE}

corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                    result=c("none", "html", "latex")){
 
   #Compute correlation matrix
  require(Hmisc)
  x <- as.matrix(x)
  correlation_matrix<-rcorr(x, type=method[1])
  R <- correlation_matrix$r # Matrix of correlation coeficients
  p <- correlation_matrix$P # Matrix of p-value 
  
  ## Define notions for significance levels; spacing is important.
  mystars <- ifelse(p < .0001, "****", ifelse(p < .001, "*** ", ifelse(p < .01, "**  ", ifelse(p < .05, "*   ", "    "))))
  
  ## trunctuate the correlation matrix to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
  
  ## build a new matrix that includes the correlations with their apropriate stars
  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
  diag(Rnew) <- paste(diag(R), " ", sep="")
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep="")
  
  ## remove upper triangle of correlation matrix
  if(removeTriangle[1]=="upper"){
    Rnew <- as.matrix(Rnew)
    Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew)
  }
  
  ## remove lower triangle of correlation matrix
  else if(removeTriangle[1]=="lower"){
    Rnew <- as.matrix(Rnew)
    Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
    Rnew <- as.data.frame(Rnew)
  }
  
  ## remove last column and return the correlation matrix
  Rnew <- cbind(Rnew[1:length(Rnew)-1])
  if (result[1]=="none") return(Rnew)
  else{
    if(result[1]=="html") print(xtable(Rnew), type="html")
    else print(xtable(Rnew), type="latex") 
  }
} 

knitr::kable(
  corstars(myraw[,c("VPDIF", "SEGM", "NETWDIF", "REVDIF", "SPINDIF", "INTCULT", "CP", "BP")]), booktabs = TRUE, 
  caption = "Correlation table, all variables (condition)."
)

```
  
  